Carp\'{e} Data: Supporting Serendipitous Data Integration in Personal Information Management

### 2012-09-14 chi2012.tex

@@

\subsection{PS.2 - Technical Challenges of Integrating the Data}
Our investigation of integration challenges started with identifying a set of data sources to analyze.  For this, we consulted the ProgrammableWeb API directory\footnote{ProgrammableWeb - \url{http://www.programmableweb.com/apis/directory}} and looked at the 50 most popular data feeds, based upon number of developer API keys issued for each.  In order to get a variety of different kinds of sources represented, we feeds pertaining to 5 topics: social networks (people), retail (shopping), events (calendar events, happenings, etc), music, and weather.   Table The second took a look at the structured data available via popular APIs, data feeds and downloadable data sets in order to characterise and understand challenges of combining data from these sources.

We first sought out the APIs and data feeds of popular Web services and sites that were aimed at developers creating apps for end-users.  Based on statistics collected We first selected 4 different categories

%% TODO THIS IS PLACEHOLDER DATA >> 
\begin{table*}
\small
\begin{tabular}{| p{2.0cm} | p{1.5cm} | p{3.6cm} | p{2cm} | p{2cm} | l | l | l |}
\hline
source category  & data type & sources & API type & avg fields/rec & avg depth & term. het & struc. het \\
\hline
social networking  & person's profile & Facebook, LinkedIn, Google+ & REST (JSON/XML) & 10 & 1.2 & 0.90 & 0.10 \\
event calendars & events & eventbrit, gcal  & REST (JSON/XML) & 10 & 1.2 & 0.90 & 0.10 \\
retail (shopping)  & product profile & Amazon, shopping.com, Etsy, Groupon, Zappos  & REST (JSON/XML) & 10 & 1.2 & 0.90 & 0.10 \\
music catalogues & songs and albums & echonest, rdio, soundcloud, spotify  & REST (JSON/XML) & 10 & 1.2 & 0.90 & 0.10 \\
weather & forecasts & wunderground, weatherbug, yahoo weather & REST (JSON/XML) & 10 & 1.2 & 0.90 & 0.10 \\
\hline
\end{tabular}
\caption{\emph{PS.2 Results} - Analysis of heterogeneity present across data feeds, by category of feed} \label{tbl_tps}
\end{table*}
%% <<

>>>>

% blargh. this needs to be integrated above! 
In order to support our primary motivation to allow users to effectively consolidate and work with data from multiple sources, we performed an exploratory sequential mixed-method investigation to help us design our contribution.  For our first pre-study we designed a semi-structured interview about which tasks and the processes people use to perform a task requiring multiple websites (see Section \ref{sec:prestudy1}).  We analysed the data collected from this study using a thematic approach.  From our first pre-study's qualitative analysis, we then designed our second pre-study which investigates the data and data formats available for people to use from popular websites (see Section \ref{sec:prestudy2}).  We performed a statistical analysis of the features of the available data.  In the next two sections, we describe our two pre-studies.

The second study we performed an analysis on existing on data available from APIs and structured data feeds on the Web.  The purpose of this study was to identify the degree of technical difficulty of integrating data from these sources.   We describe our methodology below.

@@

%% TODO THIS IS PLACEHOLDER DATA >> 
\begin{table*}
\small
\begin{tabular}{| p{2.0cm} | p{1.5cm} | p{3.6cm} | p{2cm} | p{2cm} | l | l | l |}
\hline
source category  & data type & sources & API type & avg fields/rec & avg depth & term. het & struc. het \\
\hline
social networking  & person's profile & Facebook, LinkedIn, Google+ & REST (JSON/XML) & 10 & 1.2 & 0.90 & 0.10 \\
event calendars & events & Eventbrite, Google Calendar  & REST (JSON/XML) & 10 & 1.2 & 0.90 & 0.10 \\
retail (shopping)  & product profile & Amazon, Shopping.com, Etsy, Groupon, Zappos  & REST (JSON/XML) & 10 & 1.2 & 0.90 & 0.10 \\
music catalogues & songs and albums & Echonest, rdio, Soundcloud, Spotify  & REST (JSON/XML) & 10 & 1.2 & 0.90 & 0.10 \\
weather & forecasts & W.Underground, Weatherbug, Yahoo! Weather & REST (JSON/XML) & 10 & 1.2 & 0.90 & 0.10 \\
\hline
\end{tabular}
\label{tbl:prestudy2}
\caption{\emph{PS.2 Results} - Analysis of heterogeneity present across data feeds, by category of feed} \label{tbl_tps}
\end{table*}
%% <<

\subsection{PS.2 - Technical Challenges Data Integration}
Our investigation of integration challenges started with identifying a set of candidate data sources for analysis.  For this, we consulted the ProgrammableWeb API directory\footnote{ProgrammableWeb - \url{http://www.programmableweb.com/apis/directory}} of 50 most popular data feeds measured by the number of developer API keys issued for each.  In order to get a variety of different kinds of sources represented, we first categorised feeds into 5 topic categories: social networks (people), retail (shopping), events (calendar events, happenings, etc), music, and weather. We then populated each category with 2-5 feeds each depending on feed availability, for a total of 15 total feeds.

For each feed, 3-5 data records were obtained by querying the API directly for records of a that category's primary \emph{corresponding type}, listed in the second colum of Table \ref{tbl:prestudy2}; that is, while many of the APIs also provided access to other kinds of data; for example, \url{shopping.com} offers programmatic access to ``offers'' in addition to particular product descriptions, Amazon offers access to the shopper's profile, etc, but only product records were obtained for
